The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-29 figures/scheduleChart.tex
change without design.tex

\draw (7.5cm,-7mm) node{$r_4$, initial capacity = 10, type = 3};
\draw[yshift=6.5cm] (7.5cm,-7mm) node{$r_3$, initial capacity = 10, type = 3};
\draw[yshift=13cm] (7.5cm,-7mm) node{$r_2$, initial capacity = 10, type = 2};
\draw[yshift=19.5cm] (7.5cm,-7mm) node{$r_1$, initial capacity = 10, type = 1};

>>>>

\draw[yshift=6.5cm] (7.5cm,-11mm) node{$r_4$, initial capacity = 10, type = 3};
\draw[yshift=13cm] (7.5cm,-11mm) node{$r_3$, initial capacity = 10, type = 3};
\draw[yshift=19.5cm] (7.5cm,-11mm) node{$r_2$, initial capacity = 10, type = 2};
\draw[yshift=26cm] (7.5cm,-11mm) node{$r_1$, initial capacity = 10, type = 1};

### 2016-08-29 review.tex
change without design.tex

% !TEX root = Eco-Model.tex
\section{Literature review and the knowledge gap} % (fold)
\label{sec:literature_review}
demonstrates that you know the field, justifies the reason for your research, allows you establish your theoretical and needs to be done.

XXX has been studied extensively in the literature....
\subsection{Cloud manufacturing} % (fold)
\label{sub:cloud_manufacturing review}
% This definition is quite abstract and thus despite its corretness not very useful.
from \textbf{function, resource}, information, process view to depict the cloud manufacturing platform.

@@

\textbf{Services and Tasks}

Cloud Manufacturing Ecosystem provides a platform which distributed manufacturing resources/orders gathered as resources/orders hub. In order to complete orders precisely, order will be splited into tasks. Similarly, resources will be bundled into services for the quick searhing.

\textbf{Roles}

Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
\item Users/Customers,
\item Application providers and
\item Physical resource providers.
\end{inparaenum}
However, the roles in real world always not go like this model, since it parted roles only by their functions. While, users could get different function roles depend on what transaction they take, we should make some modifiacations on this model.

% subsection cloud_manufacturing (end)

\subsection{Manufacturing ecosystem} % (fold)
\label{sub:manufacturing_ecosystem}
% xx of an ecosystem is a path-dependent, chaotic process, which means that a small difference in starting values can cause great difference to result.

% From a bionomic perspective, organisms and organizations are nodes in networks of relationships. As time passes and evolution proceeds, some nodes are wiped out and new ones crop up, triggering adjustments that ripple across each network.
\subsubsection{Different ecosystem analogies}

\subsubsection{Manufacturing system}
% Constrained by its key relationships, each organism and each organization is held in its niche, pursuing the same goal -- the genetic or technological information it carries.

% coevolved to form a vast living ecosystem

% 4 different stages for ecosystem:
% birth, expansion, leadership, final(self-renew or death)

% the major difference between ecological and social system is the role of conscious choice.

% Accoring to xxx there are three critical success factors of a business ecosystem.
% First, productivity
% Second, Robustness
% Third, have the ability to create niches and opportunities for new firms.

% Complexity relevant concepts

% Self-organization
% Emergence
% Coevolution
% adaptation

% subsection manufacturing_ecosystem (end)

\subsection{Operation model in cloud manufacturing}
\label{sub:Operation model in cloud manufacturing}

\subsection{Study of evolution on related fields} % (fold) 这段标题后期需要修改，要描述的是和演化相关的内容。
\label{sub:complex_system}
\subsubsection{System Dynamic}

\subsubsection{Agent-based Modeling}
% subsection complex_system (end)
% section literature_review (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Literature review and background} % (fold)
\label{sec:literature_review}
\subsection{Cloud manufacturing and its operation mode} % (fold)
\label{sub:cloud_manufacturing review}
% This definition is quite abstract and thus despite its corretness not very useful.

Review on 1. Cloud manufacturing mode (any) study 
2. res ser combination and decision making
3. rank and review ecosystem (system changing)
4. manufacturing system simulation

@@

Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions. For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on

Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
\item Users/Customers,
\item Application providers and
\item Physical resource providers.
\end{inparaenum}

\subsection{Study background} % (fold)
\label{sub:background}

here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
\begin{itemize}
	\item order
	\item task correspond to capacity
	\item resource
	\item capacity is the function of a resource. like quantity
	\item service is the bundle of capacities. the proportion of the capacities.
	\item 
\end{itemize}

Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment

As defined above, Enterprise User is the special case of the User(short for Generalized User) that purely provides manufacturing services and the Customer User is similarly defined.

Hence, there is only two roles in the Ecosystem worth to be studied: User and Administrator, the proportion of user type could be adjusted as the runtime of the system goes by.

% section literature_review (end)
